---
title: "Power and Sample Size Calculation Tools"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{examples}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(pwrss)
```

To install and load `pwrss`:
```{r,  message = FALSE, eval = FALSE}
install.packages("pwrss")
library(pwrss)
```

`pwrss` R package allows statistical power and minimum required sample size calculations for 

  - `(1)` testing a proportion (one-sample) against a constant, 
  - `(2)` testing a mean (one-sample) against a constant,  
  - `(3)` testing difference between two proportions (independent samples),
  - `(4)` testing difference between two means (independent and paired samples),
  - `(5)` testing a correlation (one-sample) against a constant,  
  - `(6)` testing difference between two correlations (independent samples),
  - `(7)` testing an R-squared against zero in linear regression 
  - `(8)` testing an R-squared difference against zero in hierarchical regression,
  - `(9)` testing an eta-squared or f-squared (for main and interaction effects) against zero in analysis of variance (ANOVA) (could be one-way, two-way, and three-way), 
  - `(10)` testing an eta-squared or f-squared (for main and interaction effects) against zero in analysis of covariance (ANCOVA) (could be one-way, two-way, and three-way), 
  - `(11)` testing an eta-squared or f-squared (for between, within, and interaction effects) against zero in one-way repeated measures analysis of variance (RM-ANOVA) (with non-sphericity correction and repeated measures correlation). 
  
  Alternative hypothesis can be formulated as "not equal", "less", "greater",  "non-inferior", "superior", or "equivalent" in `(1)`, `(2)`, `(3)`, and `(4)`;
  as "not equal", "less", or "greater" in `(5)` and `(6)`; but always as "greater" in `(7)`, `(8)`, `(9)`, `(10)`, and `(11)`. 


** One-way, Two-way, and Three-way Analysis of Variance (ANOVA) or Analysis of Covariance (ANCOVA)**

```{r, message = FALSE, fig.width = 7, fig.height = 5, results = TRUE}

# one-way ANOVA
pwrss.f.ancova(n.levels = 2, n.covariates = 0,
               power = .80, eta2 = 0.10)
# one-way ANCOVA
pwrss.f.ancova(n.levels = 2, n.covariates = 1,
               power = .80, eta2 = 0.08)

# two-way ANOVA
pwrss.f.ancova(n.levels = c(2,3), n.covariates = 0,
               power = .80, eta2 = 0.10)
# two-way ANCOVA
pwrss.f.ancova(n.levels = c(2,3), n.covariates = 1,
               power = .80, eta2 = 0.08)

# three-way ANOVA
pwrss.f.ancova(n.levels = c(2,3,2), n.covariates = 0,
               power = .80, eta2 = 0.10)
# three-way ANCOVA
pwrss.f.ancova(n.levels = c(2,3,2), n.covariates = 1,
               power = .80, eta2 = 0.08)

```

** One-way Repeated Measures Analysis of Variance (RM-ANOVA)**

```{r, message = FALSE, fig.width = 7, fig.height = 5, results = TRUE}

pwrss.f.rmanova(eta2 = 0.10,  n.levels = 2, n.measurements = 3,
                 repmeasures.r = 0.50, type = "between", power = 0.80)

pwrss.f.rmanova(eta2 = 0.10,  n.levels = 2, n.measurements = 3,
                repmeasures.r = 0.50, epsilon = 1,
                type = "within", power = 0.80)

pwrss.f.rmanova(eta2 = 0.10,  n.levels = 2, n.measurements = 3,
                repmeasures.r = 0.50, epsilon = 1,
                type = "interaction", power = 0.80)

```

--o--
